Algebraic File Synchronization: Adequacy and Completeness

### 2018-01-29 p2/axioms.tex
Revisions

% TODO Rewrite script for new notation

\myskip
Command pairs in genral have the form
\[ \cxynv\cc  \czwmv \]
where $x,y,z,w\in\setv$ and $n,m\in\setn$.

@@

\begin{mydef}[Construction pair]
A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
and the commands are one
of the following:
   \begin{align*}
            \cbda{\nn}&\cc  \cbfa{n} \\
            \cbda{\nn}&\cc  \cbda{n} \\
            \cfda{\nn}&\cc  \caaa{\empt}{\valff}{n} \\
            \cfda{\nn}&\cc  \cbda{n}
   \end{align*}
\end{mydef}

@@

\begin{mydef}[Destruction pair]
A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
of the following:
   \begin{align*}
            \cfba{n}&\cc  \cdba{\nn} \\
            \cfba{n}&\cc  \caaa{\vald}{\valff}{\nn} \\
            \cdba{n}&\cc  \cdba{\nn} \\
            \cdba{n}&\cc  \cdfa{\nn}
   \end{align*}
\end{mydef}

>>>>

\myskip
Command pairs in genral have the form
\[ \cxynv\cc  \czwmv \]
where $x,y,z,w\in\setv$ and $n,m\in\setn$. 
Extending \cref{def:command_categories}, we call certain pairs
\emph{construction} or \emph{destruction pairs}.

\begin{mydef}[Construction and destruction pairs]
A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parentf{n}$ 
and the commands are one
of the following:
   \begin{align*}
            \cbda{\nn}&\cc  \cbfa{n} \\
            \cbda{\nn}&\cc  \cbda{n} \\
            \cfda{\nn}&\cc  \caaa{\empt}{\valff}{n} \\
            \cfda{\nn}&\cc  \cbda{n}
   \end{align*}
\end{mydef}

\begin{mydef}[Destruction pair]
A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parentf{n}=\nn$ and the commands are one
of the following:
   \begin{align*}
            \cfba{n}&\cc  \cdba{\nn} \\
            \cfba{n}&\cc  \caaa{\vald}{\valff}{\nn} \\
            \cdba{n}&\cc  \cdba{\nn} \\
            \cdba{n}&\cc  \cdfa{\nn}
   \end{align*}
\end{mydef}

@@

@@

### 2018-01-29 p2/def-commands.tex
Revisions

\myskip
Depending on their input and output types, there are nine types of commands,
which we separate into four categories depending on the overall effect of the command.
Constructions commands extend the filesystem,
while destruction commands shrink it;
the replacement command replaces a file value with a (presumably different) file value,
and assertion commands either break the filesystem, or assert the type of the value at a node.
\begin{mydef}[Command categories]
Depending on their input and output types, filesystem commands
belong to exactly one of the following four categories:
\begin{itemize}
\item[]\emph{Construction commands:}
    $\cbfa{n}$, $\cbda{n}$ and $\cfda{n}$;
\item[]\emph{Destruction commands:}
    $\cdfa{n}$, $\cdba{n}$ and $\cfba{n}$;
\item[]\emph{Assertion commands:}
    $\cbba{n}$ and $\cdda{n}$;
\item[]\emph{Replacement command:}
    $\caaa{\valfx}{\valff}{n}$.
\qedhere
\end{itemize}
\end{mydef}

>>>>

\myskip
Depending on their input and output types, there are nine types of commands,
which we separate into four categories depending on the overall effect of the command.
Constructions commands extend the filesystem,
while destruction commands shrink it;
the replacement command replaces a file value with a (presumably different) file value,
and assertion commands either break the filesystem, or assert the type of the value at a node.
\begin{mydef}[Command categories]\mlabel{def:command_categories}
Depending on their input and output types, filesystem commands
belong to exactly one of the following four categories:
\begin{itemize}
\item[]\emph{Construction commands:}
    $\cbfa{n}$, $\cbda{n}$ and $\cfda{n}$;
\item[]\emph{Destruction commands:}
    $\cdfa{n}$, $\cdba{n}$ and $\cfba{n}$;
\item[]\emph{Assertion commands:}
    $\cbba{n}$ and $\cdda{n}$;
\item[]\emph{Replacement command:}
    $\caaa{\valfx}{\valff}{n}$.
\qedhere
\end{itemize}
\end{mydef}
